---
title             : "Discussion"
shorttitle        : "Moral Dilution"
author:
  - name          : "Cillian McHugh"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University of Limerick, Limerick, Ireland, V94 T9PX"
    email         : "cillian.mchugh@ul.ie"
  - name          : "Eric R. Igou"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "University of Limerick"
author_note: >
  All procedures performed in studies involving human participants were approved by institutional research ethics committee and conducted in accordance with the Code of Professional Ethics of the Psychological Society of Ireland, and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards. Informed consent was obtained from all individual participants included in the study. The authors declare that there are no potential conflicts of interest with respect to the research, authorship, and/or publication of this article. All authors consented to the submission of this manuscript.
abstract: >
  Six studies etc.
keywords          : "keywords"
wordcount         : "TBC"
bibliography: "../resources/bib/My Library.bib"
csl: "../resources/bib/apa6.csl"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
toc               : no
lang              : "en-US"
documentclass     : "apa7"
output:
  papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r Discussionsetup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
# knitr::opts_chunk$set(eval = TRUE, echo = TRUE)
#knitr::opts_chunk$set(include = FALSE)
```


```{r}
library("papaja")
library(metap)
library(desnum)
#library("wordcountaddin")
#wordcountaddin::word_count("Introduction.Rmd")
getwd()
#devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)
```

# Aggregate Results

```{r}
#### Overall dilution effect ####

# all_ps <-
#   c(# MPS-4  MM-1
#      .0001, .0001  # Study 1
#     ,.624 , .267   # Study 2
#     ,.060 , .008   # Study 3 Bad
#     ,.009 , .0001  # Study 3 Good
#     ,.095 , .029   # Study 4
#     ,.221 , .140   # Study 5 Bad
#     ,.002 , .0001  # Study 5 Good
# )

load("S1_effect_stats.RData")
load("S2_effect_stats.RData")
load("S3_effect_stats.RData")
load("supp_S1_effect_stats.RData")
load("supp_S2_effect_stats.RData")
load("supp_S3_effect_stats.RData")



m_fun <- function(x){deparse(substitute(x))
  m <- x
  
  c(
    m$study,
    as.numeric(m$x1)
    ,as.numeric(m$x2)
    ,as.numeric(m$s1)
    ,as.numeric(m$s2)
    ,as.numeric(m$n1)
    ,as.numeric(m$n2)
    ,as.numeric(m$s_pooled)
    ,as.numeric(m$d)
    ,as.numeric(m$vd)
    ,as.numeric(m$sed)
    ,as.numeric(m$ci_upper)
    ,as.numeric(m$ci_lower)
    ,as.numeric(m$p)
    ,as.numeric(m$d_paired))
}

# m_fun <- function(x){deparse(substitute(x))}

test_bad_rtot <- `colnames<-`(
  rbind.data.frame(
    m_fun(s1_rtot_stats)
    ,m_fun(s3bad_rtot_stats)
    # ,m_fun(supp_s2bad_rtot_stats)
    # ,m_fun(supp_s3bad_rtot_stats)
  ),
  names(s1_rtot_stats))


test_good_rtot <- `colnames<-`(
  rbind.data.frame(
    m_fun(s2_rtot_stats)
    ,m_fun(s3good_rtot_stats)
    # ,m_fun(supp_s1_rtot_stats)
    # ,m_fun(supp_s2good_rtot_stats)
    # ,m_fun(supp_s3good_rtot_stats)
  ),
  names(s1_rtot_stats))



test_bad_M1 <- `colnames<-`(
  rbind.data.frame(
    m_fun(s1_M1_stats)
    ,m_fun(s3bad_M1_stats)
    # ,m_fun(supp_s2bad_M1_stats)
    # ,m_fun(supp_s3bad_M1_stats)
  ),
  names(s1_rtot_stats))


test_good_M1 <- `colnames<-`(
  rbind.data.frame(
    m_fun(s2_M1_stats)
    ,m_fun(s3good_M1_stats)
    # ,m_fun(supp_s1_M1_stats)
    # ,m_fun(supp_s2good_M1_stats)
    # ,m_fun(supp_s3good_M1_stats)
  ),
  names(s1_rtot_stats))


test_good_both <- `colnames<-`(
  rbind.data.frame(
    m_fun(s2_M1_stats)
    ,m_fun(s3good_M1_stats)
    ,m_fun(supp_s1_M1_stats)
    ,m_fun(supp_s2good_M1_stats)
    ,m_fun(supp_s3good_M1_stats)
    ,m_fun(s2_rtot_stats)
    ,m_fun(s3good_rtot_stats)
    ,m_fun(supp_s1_rtot_stats)
    ,m_fun(supp_s2good_rtot_stats)
    ,m_fun(supp_s3good_rtot_stats)
  ),
  names(s1_rtot_stats))


test_good_both$measure <- c(
  rep("MM-1",5),
  rep("MPS-4",5)
)



x <- test_good_both

x$studyorder <- c(2,3,4,5,6,2,3,4,5,6)  

x <- x[order(x$studyorder),]


paste(x$study,": ",x$measure, sep = "")

x$valence <- rep("good")

x$lab <- paste(x$study,": ",x$measure, " - ", x$valence, sep = "")


test_good_both <- x

test_bad_both <- `colnames<-`(
  rbind.data.frame(
    m_fun(s1_M1_stats)
    ,m_fun(s3bad_M1_stats)
    # ,m_fun(supp_s1_M1_stats)
    ,m_fun(supp_s2bad_M1_stats)
    ,m_fun(supp_s3bad_M1_stats)
    ,m_fun(s1_rtot_stats)
    ,m_fun(s3bad_rtot_stats)
    # ,m_fun(supp_s1_rtot_stats)
    ,m_fun(supp_s2bad_rtot_stats)
    ,m_fun(supp_s3bad_rtot_stats)
  ),
  names(s1_rtot_stats))

test_bad_both$measure <- c(
  rep("MM-1",4),
  rep("MPS-4",4)
)


x <- test_bad_both

x$studyorder <- c(1,3,5,6,1,3,5,6)  

x <- x[order(x$studyorder),]


paste(x$study,": ",x$measure, sep = "")


x$valence <- rep("bad")

x$lab <- paste(x$study,": ",x$measure, " - ", x$valence, sep = "")

test_bad_both <- x


test_both <- rbind.data.frame(test_good_both,test_bad_both)
sqrt(as.numeric(test_both$d)*as.numeric(test_both$d))

test_both$d_absolute <- sqrt(as.numeric(test_both$d)*as.numeric(test_both$d))

# meta-analysis with continuout outcome
# comb.fixed/comb.random: indicator whether a fix/random effect mata-analysis to be conducted.
# sm: Three different types of summary measures to choose,standardized mean difference (SMD),mean difference (MD), ratio of means (ROM)
meta1 =  meta::metacont(as.numeric(n1), as.numeric(x1), as.numeric(s1), 
                        as.numeric(n2), as.numeric(x2), as.numeric(s2),
                        common = T , random = T, studlab = study,
                        data = test_bad_rtot, sm = "SMD") 
meta2 =  meta::metacont(as.numeric(n1), as.numeric(x1), as.numeric(s1), 
                        as.numeric(n2), as.numeric(x2), as.numeric(s2),
                        common = T , random = T, studlab = study,
                        data = test_bad_M1, sm = "SMD") 
meta3 =  meta::metacont(as.numeric(n1), as.numeric(x1), as.numeric(s1), 
                        as.numeric(n2), as.numeric(x2), as.numeric(s2),
                        common = T , random = T, studlab = study,
                        data = test_good_rtot, sm = "SMD") 
meta4 =  meta::metacont(as.numeric(n1), as.numeric(x1), as.numeric(s1), 
                        as.numeric(n2), as.numeric(x2), as.numeric(s2),
                        common = T , random = T, studlab = study,
                        data = test_good_M1, sm = "SMD") 
meta5 =  meta::metacont(as.numeric(n1), as.numeric(x1), as.numeric(s1), 
                        as.numeric(n2), as.numeric(x2), as.numeric(s2),
                        common = T , random = T, studlab = study,
                        data = test_good_both, sm = "SMD") 
meta6 =  meta::metacont(as.numeric(n1), as.numeric(x1), as.numeric(s1), 
                        as.numeric(n2), as.numeric(x2), as.numeric(s2),
                        common = T , random = T, studlab = study,
                        data = test_bad_both, sm = "SMD") 

summary(meta1)
summary(meta2)
summary(meta3)
summary(meta4)
summary(meta5)
summary(meta6)



meta::forest(meta1, leftcols=c("studlab"))
meta::forest(meta2, leftcols=c("studlab"))
meta::forest(meta3, leftcols=c("studlab"))
meta::forest(meta4, leftcols=c("studlab"))
meta::forest(meta5, leftcols=c("studlab"))
meta::forest(meta6, leftcols=c("studlab"))

#####

# install.packages("dmetar")
library(metafor)

x <- test_both
x <- x[order(x$studyorder),]

x$ntot <- as.numeric(x$n1)+as.numeric(x$n2)

#x <- x[1:8,]
x <- x[which(x$valence=="good"),]

# escalc(measure="MC"
#        ,x1i=as.numeric(n1)
#        ,x2i=as.numeric(n2)
#        ,m1i=as.numeric(x1)
#        ,m2i=as.numeric(x2)
#        ,sd1i=as.numeric(s1)
#        ,sd2i=as.numeric(s2)
#        ,data=x)

x$d_paired_absolute <- sqrt(as.numeric(x$d_paired)*as.numeric(x$d_paired))

m_multi <- metafor::rma.mv(as.numeric(d_paired_absolute),
                  as.numeric(vd),
                  W=ntot,# (n1+n2),
                  slab = lab,
                  random = ~ 1 | study/measure/valence,
                  method = "ML",
                  test = "z",
                  dfs = "contain",
                  data = x) 

summary(m_multi)

metafor::forest(m_multi)



x <- test_bad_both

x$ntot <- as.numeric(x$n1)+as.numeric(x$n2)

x <- x[order(x$studyorder),]

m_multi <- metafor::rma.mv(as.numeric(d_paired),
                  as.numeric(vd),
                  W = ntot,
                  slab = lab,
                  random = ~ 1 | study/measure,
                  method = "REML",
                  test = "z",
                  dfs = "contain",
                  data = x) 



summary(m_multi)


meta::forest(m_multi)



x <- test_good_both

x$ntot <- as.numeric(x$n1)+as.numeric(x$n2)

x <- x[order(x$studyorder),]

m_multi <- metafor::rma.mv(as.numeric(d_paired),
                  as.numeric(vd),
                  W = ntot,
                  slab = lab,
                  random = ~ 1 | study/measure,
                  method = "REML",
                  test = "z",
                  dfs = "contain",
                  data = x) 


summary(m_multi)



meta::forest(m_multi)


m_multi <- metafor::rma.mv(as.numeric(d),
                  as.numeric(vd),
                  W = ntot
                  slab = lab,
                  random = ~ 1 | study/measure,
                  method = "REML",
                  test = "z",
                  dfs = "contain",
                  data = test_bad_both) 

summary(m_multi)

metafor::forest(m_multi)

meta::forest(m_multi)


full.model <- rma.mv(yi = z, 
                     V = var.z, 
                     slab = author,
                     data = Chernobyl,
                     random = ~ 1 | author/es.id, 
                     test = "t", 
                     method = "REML")



all_ps <-
  c(# MPS-4  MM-1
     .0001, .0001  # Study 1
    ,.624 , .267   # Study 2
    ,.0001 , .0001   # Study 3 Bad
    ,.0001 , .0001  # Study 3 Good
)

# all_ps_mm1 <-
#   c(# MPS-4  MM-1
#     # .0001
#              .0001  # Study 1
#     #,.624 
#             , .267   # Study 2
#     #,.060 
#             , .008   # Study 3 Bad
#     #,.009 
#             , .0001  # Study 3 Good
#     #,.095 
#             , .029   # Study 4
#     #,.221 
#             , .140   # Study 5 Bad
#     #,.002 
#             , .0001  # Study 5 Good
# )



all_ps_mm1 <-
  c(# MPS-4  MM-1
    # .0001
             .0001  # Study 1
    #,.624 
            , .267   # Study 2
    #,.060 
            , .0001   # Study 3 Bad
    #,.009 
            , .0001  # Study 3 Good
)


all_ps_m4 <-
  c(# MPS-4  MM-1
     .0001#, .0001  # Study 1
    ,.624 #, .267   # Study 2
    ,.0001 #, .008   # Study 3 Bad
    ,.0001 #, .0001  # Study 3 Good
)

all_ns <- 
  c(
    # MPS-4  MM-1
     801 #, 801   # Study 1
    ,820 #, 820   # Study 2
    ,814 #, 874   # Study 3 Bad
    ,814 #, 874   # Study 3 Good
    # ,856 #, 856   # Study 4
    # ,860 #, 860   # Study 5 Bad
    # ,890 #, 890   # Study 5 Good
  )

meta3 <- sumlog(all_ps)
meta3

all_ps_mm1
meta3 <- sumlog(all_ps_mm1)
meta3

all_ps_m4
meta3 <- sumlog(all_ps_m4)
meta3



psch5 <- all_ps
wtsch5 <- sqrt(all_ns)

meta4 <- sumz(psch5,wtsch5)
meta4

psch5 <- all_ps_mm1
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4

psch5 <- all_ps_m4
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4


###### for reporting #####

meta3 <- sumlog(all_ps)
meta3

psch5 <- all_ps
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4

```

A mini meta-analysis and found a significant dilution effect across both good and bad character descriptions across all studies  $\chi$^2^(`r meta3$df`) = `r round(meta3$chisq, digits=3)`, *p* `r paste(p_report(meta3$p))` (Fisher’s method); or when weighting for sample size, *z* `r paste(p_report(meta4$z))`, *p* `r paste(p_report(meta4$p))` (Stouffer's Z-score method).



```{r}
#### Bad dilution effect ####

all_ps <-
  c(# MPS-4  MM-1
     .0001, .0001  # Study 1
  # ,.624 , .267   # Study 2
    ,.0001 , .0001   # Study 3 Bad
  # ,.009 , .0001  # Study 3 Good
  # ,.095 , .029   # Study 4
  #  ,.221 , .140   # Study 5 Bad
  # ,.002 , .0001  # Study 5 Good
)




all_ps_mm1 <-
  c(# MPS-4  MM-1
   # .0001
             .0001  # Study 1
  ##,.624 
          #, .267   # Study 2
   #,.060 
          , .0001   # Study 3 Bad
  ##,.009 
          #, .0001  # Study 3 Good
  ##,.095 
          #, .029   # Study 4
   #,.221 
#           , .140   # Study 5 Bad
  ##,.002 
          #, .0001  # Study 5 Good
)



all_ps_m4 <-
  c(# MPS-4  MM-1
     .0001#, .0001  # Study 1
  # ,.624 #, .267   # Study 2
    ,.0001 #, .008   # Study 3 Bad
  # ,.009 #, .0001  # Study 3 Good
  # ,.095 #, .029   # Study 4
    # ,.221 #, .140   # Study 5 Bad
  # ,.002 #, .0001  # Study 5 Good
)


all_ns <- 
  c(
    # MPS-4  MM-1
     801 #, 801   # Study 1
  # ,820 #, 820   # Study 2
    ,814 #, 874   # Study 3 Bad
  # ,874 #, 874   # Study 3 Good
  # ,856 #, 856   # Study 4
  #  ,860 #, 860   # Study 5 Bad
  # ,890 #, 890   # Study 5 Good
  )


all_ps_m4

meta3 <- sumlog(all_ps)
meta3

meta3 <- sumlog(all_ps_mm1)
meta3

meta3 <- sumlog(all_ps_m4)
meta3


psch5 <- all_ps
wtsch5 <- sqrt(all_ns)

meta4 <- sumz(psch5,wtsch5)
meta4


psch5 <- all_ps_mm1
wtsch5 <- sqrt(all_ns)

meta4 <- sumz(psch5,wtsch5)
meta4


psch5 <- all_ps_m4
wtsch5 <- sqrt(all_ns)

meta4 <- sumz(psch5,wtsch5)
meta4


###### for reporting #####

meta3 <- sumlog(all_ps)
meta3

psch5 <- all_ps
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4


```

A mini meta-analysis and found a significant dilution effect for bad character descriptions across all studies  $\chi$^2^(`r meta3$df`) = `r round(meta3$chisq, digits=3)`, *p* `r paste(p_report(meta3$p))` (Fisher’s method); or when weighting for sample size, *z* `r paste(p_report(meta4$z))`, *p* `r paste(p_report(meta4$p))` (Stouffer's Z-score method).


```{r}
#### Good dilution effect ####

all_ps <-
  c(# MPS-4  MM-1
  #  .0001, .0001  # Study 1
     .624 , .267   # Study 2
  # ,.060 , .008   # Study 3 Bad
    ,.0001 , .0001  # Study 3 Good
  #   ,.095 , .029   # Study 4
  # # ,.221 , .140   # Study 5 Bad
  #   ,.002 , .0001  # Study 5 Good
)


all_ps_mm1 <-
  c(# MPS-4  MM-1
  # # .0001
          #, .0001  # Study 1
    # .624 
           .267   # Study 2
  # #,.060 
          #, .008   # Study 3 Bad
    #,.009 
          , .0001  # Study 3 Good
  #   #,.095 
  #         , .029   # Study 4
  # # #,.221 
  #         #, .140   # Study 5 Bad
  #   #,.002 
  #         , .0001  # Study 5 Good
)

all_ps_m4 <-
  c(# MPS-4  MM-1
  #  .0001#, .0001  # Study 1
     .624 #, .267   # Study 2
  # ,.060 #, .008   # Study 3 Bad
    ,.0001 #, .0001  # Study 3 Good
  #   ,.095 #, .029   # Study 4
  # # ,.221 #, .140   # Study 5 Bad
  #   ,.002 #, .0001  # Study 5 Good
)


all_ns <- 
  c(
    # MPS-4  MM-1
  #  801 #, 801   # Study 1
     820 #, 820   # Study 2
  # ,874 #, 874   # Study 3 Bad
    ,814 #, 874   # Study 3 Good
  #   ,856 #, 856   # Study 4
  # # ,860 #, 860   # Study 5 Bad
  #   ,890 #, 890   # Study 5 Good
  )

#meta3 <- sumlog(c(.023,.021,.039,.359,.215,.000002925))
meta3 <- sumlog(all_ps)
meta3

meta3 <- sumlog(all_ps_mm1)
meta3

meta3 <- sumlog(all_ps_m4)
meta3

psch5 <- all_ps
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4

psch5 <- all_ps_mm1
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4

psch5 <- all_ps_m4
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4


###### for reporting #####

meta3 <- sumlog(all_ps)
meta3

psch5 <- all_ps
wtsch5 <- sqrt(all_ns)
meta4 <- sumz(psch5,wtsch5)
meta4


```

A mini meta-analysis and found a significant dilution effect for good character descriptions across all studies  $\chi$^2^(`r meta3$df`) = `r round(meta3$chisq, digits=3)`, *p* `r paste(p_report(meta3$p))` (Fisher’s method); or when weighting for sample size, *z* `r paste(p_report(meta4$z))`, *p* `r paste(p_report(meta4$p))` (Stouffer's Z-score method).



# Discussion













