---
title: "The Moral Dilution Effect"
authors: "Cillian McHugh & Eric R. Igou"
institute: "Department of Psychology Seminar Series"
bibliography: "../resources/bib/MyLibrary_Oct2024.bib"
csl: "../resources/bib/apa.csl"
format:
  revealjs:
    slide-number: false
    controls: true
    logo: "images/ul-psychology-logos.png"
    footer: "Cillian McHugh - 16/10/24"
    theme: "../resources/css/mytheme.scss"
    chalkboard: 
      buttons: true
editor: source
---

## Overview

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)

```

```{r}
rm(list = ls())

# library(desnum)
# library(tidyverse)

#devtools::install_github("crsh/citr")
#install.packages("car")
library(citr)
#install.packages("sjstats")
library(plyr)
library(foreign)
library(car)
#devtools::install_github("cillianmiltown/R_desnum")
library(desnum)
library(ggplot2)
library(extrafont)
#install.packages("papaja")
#devtools::install_github("crsh/papaja", force=T)
library(papaja)
#library("dplyr")
#install.packages("afex")
library("afex")
library("tibble")
library(scales)
#install.packages("metap")
#install.packages("metap")
library(metap)
#install.packages("pwr")
library(pwr)
#install.packages("lsr")
library(lsr)
#install.packages("sjstats")
library(sjstats)
#install.packages("DescTools")
library(DescTools)
#inatall.packages("ggstatsplot")
#library(ggstatsplot)
#install.packages("VGAM")
library(VGAM)
library(nnet)
#install.packages("mlogit")
library(mlogit)
library(reshape2)
library("powerMediation")
library("ggpubr")
#install.packages("powerMediation")
#library("powerMediation")
#install.packages("magick")
# install.packages("ltm")
#source("load_all_data.R")
#install.packages("magick")
#tinytex::reinstall_tinytex()
# install.packages("ltm")

#devtools::install_github("benmarwick/wordcountaddin")
#library(wordcountaddin)

#setwd("manuscript_revisions")
# getwd()
# getwd()

```

- What is the (moral) dilution effect
- The current studies
  - Study 1 (bad characters)
  - Study 2 (good characters)
  - Study 3 (bad *and* good characters)
  - (other studies 2 pilots, 3 supplementary studies)

## The Dilution Effect

- Diagnostic information about a target is ‘diluted’ by non-diagnostic information [@nisbett_dilution_1981; @kemmelmeier_does_2007; @tetlock_dilution_1996]
- Shown for
  - judging products [@igou_conversational_2005; @meyvis_consumers_2002]
  - probability judgments [@labella_dilution_2004]
  - and predictions relating to people’s behavior [@nisbett_dilution_1981; @zukier_dilution_1982]

## References

